Coming to Germany: Pre-migration language skills, Job search and Labor market outcomes

### 2018-09-02 Paper 2.tex
Update Paper 2.tex

This is an important research question because by understanding thoroughly the mechanisms through which language skills at arrival exert an influence on later labor market outcomes, policy makers can make informed decisions to improve immigrants' integration immediately after they arrive in the host countries. This paper attempts to explore the role of the pre-migration language skills on the current labor market outcomes of immigrants in Germany. More importantly, this aims to open the black-box to disentangle \textit{how} and \textit{why} language proficiency exerts its influence on labor market success of immigrants.

>>>>

This is an important research question because language skills at arrival relate to a number of important decisions immigrants have to make such as education or job search, so by understanding thoroughly the mechanisms through which language skills at arrival exert an influence on later labor market outcomes, policy makers can make informed decisions to improve immigrants' integration immediately after they arrive in the host countries. This paper attempts to explore the role of the pre-migration language skills on the current labor market outcomes of immigrants in Germany. More importantly, this aims to open the black-box to disentangle \textit{how} and \textit{why} language proficiency exerts its influence on labor market success of immigrants.
